Bioverse: Origins of Life

### 2023-12-13 src/tex/ms.tex
add true evidence plot

Hence,
\begin{equation}
BF_{H_3,H_\mathrm{3, null}} = \frac{P(Y=k|H_3)}{P(Y=k|H_\mathrm{3, null})} = \frac{\binom{n_\lambda}{k}}{\binom{n}{k}}(1-f_\mathrm{life})^{n_{\lambda}-n}.
\end{equation}

@@

\begin{figure}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/inhabited_FGKM.pdf}
        \caption{Host stars of all transiting planets, \glspl{EEC}, and inhabited planets. In a sample of \var{N_nautilus} transiting planets, most \glspl{EEC} and all inhabited planets orbit M~dwarfs.}
        \label{fig:inhabited_FGKM}
    \end{centering}
\end{figure}

@@

>>>>

Hence,
\begin{equation}\label{eq:bayes_factor}
BF_{H_3,H_\mathrm{3, null}} = \frac{P(Y=k|H_3)}{P(Y=k|H_\mathrm{3, null})} = \frac{\binom{n_\lambda}{k}}{\binom{n}{k}}(1-f_\mathrm{life})^{n_{\lambda}-n}.
\end{equation}

Given a sample of planets, where for some of them we have convincing biosignature detections but remaining agnostic on $f_\mathrm{life}$: What evidence for $H_\mathrm{3}$ and $H_\mathrm{3, null}$ can we expect to get?
Our Bayes factor (Equation~\ref{eq:bayes_factor}) is determined by the unknown variables $f_\mathrm{life}$ and $F_\mathrm{NUV, min}$, as well as the number of planets with biosignature detections in the sample $k$.
To compute the distribution of evidences, we repeatedly generated samples under $H_\mathrm{3}$ and $H_\mathrm{3, null}$ and computed the Bayes factors $BF_{H_3,H_\mathrm{3, null}}$ and $BF_{H_\mathrm{3, null}, H_3}$.
We then evaluated the fraction of Monte Carlo runs in which certain evidence thresholds~\citep{Jeffreys1939} were exceeded.

@@

\begin{figure}
    \script{inhabited_FGKM.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/inhabited_FGKM.pdf}
        \caption{Host stars of all transiting planets, \glspl{EEC}, and inhabited planets. In a sample of \var{N_nautilus} transiting planets, most \glspl{EEC} and all inhabited planets orbit M~dwarfs.}
        \label{fig:inhabited_FGKM}
    \end{centering}
\end{figure}

@@

\subsubsection{Semi-analytical approach}
In Section~\ref{sec:met-semianalytical} We computed the probability for true positive evidence for $H_\mathrm{3}$ and $H_\mathrm{3, null}$ respectively.
Figure~\ref{fig:semian_true_evidence} shows how these evidences are distributed for sample sizes \var{semian_Nsamp1} and \var{semian_Nsamp2}, and how likely we are to obtain strong evidence ($BF_{H_i, H_j}$ > 10).
For $n = \var{semian_Nsamp1}$, strong true evidence for $H_\mathrm{3}$ ($H_\mathrm{3, null}$) can be expected in $\sim \SI{30}{\percent}$ ($\sim \SI{40}{\percent}$) of all random experiments.
In the majority of cases, the outcome of the survey will be inconclusive.
\begin{figure}
    \script{semian_true_evidence.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/semian_true_evidence.pdf}
        \caption{Probability to obtain true strong evidence for $H_\mathrm{3}$ and $H_\mathrm{3, null}$ under sample sizes $n = \var{semian_Nsamp1}$ (solid) and $n = \var{semian_Nsamp2}$ (dashed). The vertical lines denote the thresholds for ``strong'' evidence, $BF_{H_i, H_j}$ > 10, and ``extreme'' evidence, $BF_{H_i, H_j}$ > 100.}
        \label{fig:semian_true_evidence}
    \end{centering}
\end{figure}
The situation improves for larger samples -- \SI{80}{\percent} of random experiments yield true strong evidence under either $H_\mathrm{3}$ or $H_\mathrm{3, null}$.

\subsubsection{Survey simulations with Bioverse}
